Resolvable Ambiguity

### 2019-07-11 paper/paper.tex
Minor fixes in section 8.

\begin{itemize}
\item $s$ and $f$ are two new distinct states.
\item $Q = \{s, f\} \cup \bigsqcup_l Q_l$.
\item $\T' = \T \cup \{\reqpl, \pospl, \pospr\}$.
\item $\Gamma = Q \times Q \times \Labels^{*}$.
\item $\delta$ is defined by the following equations (unspecified cases produce $\emptyset$):
  $$
  \begin{array}{r@{\;=\;}l@{\;\mid\;}l}
    \delta(p, a, \lambda)
    & \multicolumn{2}{@{}l@{}}{\{(\delta_l(p, a), \lambda)\} \qquad \text{ where } p \in Q_l \text{ and } a \in \T} \\

@@

% UNFINISHED

>>>>

\begin{itemize}
\item $s$ and $f$ are two new distinct states.
\item $Q = \{s, f\} \cup \bigsqcup_l Q_l$.
\item $\T' = \T \cup \{\reqpl, \pospl, \pospr\}$.
\item $\Gamma = Q \times Q \times \Labels^{*}$.
\item $\delta$ is defined by (in hindsight this should probably be written as constructing a set $\delta$, i.e., instead of a function $\delta: Q \times \T' \times (\Gamma \cup \{\lambda\}) -> 2^{Q \times (\Gamma \cup \{\lambda\})}$ we have a set $\delta \subseteq Q \times \T' \times (\Gamma \cup \{\lambda\}) \times Q \times (\Gamma \cup \{\lambda\})$, would probably be easier to read):
  $$
  \begin{array}{r@{\;=\;}l@{\;\mid\;}l}
    \delta(p, a, \lambda)
    & \multicolumn{2}{@{}l@{}}{\{(\delta_l(p, a), \lambda)\} \qquad \text{ where } p \in Q_l \text{ and } a \in \T} \\

@@

UNFINISHED
